Translation Elicitation: Report

### 2022-03-21 docs/index.Rmd
Minor refactoring

str_repl <- c(
  "Intercept" = "Intercept",
  "frequency_zipf_std" = "Frequency\n[+1 SD]",
  "pthn_std:lv_std" = "PTHN \u00d7 Levenshtein", 
  "lv_std:groupENGvs.SPA" = "Levenshtein \u00d7 Group 1",
  "lv_std:groupENGMCATvs.ENGMSPA" = "Levenshtein \u00d7 Group 2",
  "lv_std" = "Levenshtein\n[+1 SD]",
  "pthn_std" = "PTHN\n[+1 SD]",
  "groupENGvs.SPA" =  "Group 1\n[ENG-* vs. SPA-CAT]",
  "groupENGMCATvs.ENGMSPA" = "Group 2\n[ENG-CAT vs. ENG-SPA]"
)

coefs %>% 
  mutate(
    variable = str_remove(variable, "b_") %>% 
      str_replace_all(str_repl) %>%  
      factor(
        levels = c(
          "Intercept", "Frequency\n[+1 SD]", "PTHN\n[+1 SD]", 
          "Levenshtein\n[+1 SD]", "PTHN \u00d7 Levenshtein",
          "Group 1\n[ENG-* vs. SPA-CAT]",
          "Group 2\n[ENG-CAT vs. ENG-SPA]",
          "Levenshtein \u00d7 Group 1", "Levenshtein \u00d7 Group 2"
        )
      )
  ) %>% 
  select(-est_error) %>% 
  gt() %>% 
  fmt_percent(2:4) %>% 
  cols_merge(c("q2_5", "q97_5"), pattern = "[{1}, {2}]") %>% 
  cols_label(
    variable = md("**Predictor**"),
    estimate = md("**Mean**"),
    q2_5 = md("**95\\% CrI**"),
  ) %>% 
  tab_source_note("Estimated posterior distributions of coefficients in Model 6. A\\) Population-level effects. Distributions indicate the estimated posterior likelihood density of regression coefficients of fixed effects. Credible intervals (*CrI*), represented with increasingly lighter segmentents in the distribution indicate the range of values that contain the true value with 95\\%, 80\\%, and 50\\% probability. Black dots represent the mean of each distribution.") %>% 
  cols_align(align = "left") %>% 
  as_raw_html()
```

@@

str_repl <- c(
  "Intercept" = "Intercept",
  "frequency_zipf_std" = "Frequency\n[+1 SD]",
  "pthn_std:lv_std" = "PTHN \u00d7 Levenshtein", 
  "lv_std:group1" = "Levenshtein \u00d7 Group 1",
  "lv_std:group2" = "Levenshtein \u00d7 Group 2",
  "lv_std" = "Levenshtein\n[+1 SD]",
  "pthn_std" = "PTHN\n[+1 SD]",
  "group1" =  "Group 1\n[ENG-* vs. SPA-CAT]",
  "group2" = "Group 2\n[ENG-CAT vs. ENG-SPA]"
)

# fixed effects
post_fix <- posterior_draws_fixed %>% 
  filter(str_detect(.variable, "b_")) %>% 
  mutate(
    .variable_name = str_remove(.variable, "b_") %>% 
      str_replace_all(str_repl) %>%  
      factor(
        levels = c(
          "Intercept", "Frequency\n[+1 SD]", "PTHN\n[+1 SD]", 
          "Levenshtein\n[+1 SD]", "PTHN \u00d7 Levenshtein",
          "Group 1\n[ENG-* vs. SPA-CAT]",
          "Group 2\n[ENG-CAT vs. ENG-SPA]",
          "Levenshtein \u00d7 Group 1", "Levenshtein \u00d7 Group 2"
        )
      ),
    .value = ifelse(str_detect(.variable, "Intercept"), inv_logit_scaled(.value), .value/4)
  ) %>% 
  arrange(.variable) %>% 
  ggplot(aes(.value, fct_rev(.variable_name))) +
  geom_vline(xintercept = 0) +
  stat_slab(aes(fill = stat(cut_cdf_qi(cdf, .width = c(.5, .8, .95), labels = percent_format())))) +
  stat_pointinterval(.width = 0, point_size = 1) +
  scale_fill_manual(values = c("#1A85FF", "#9ccaff", "#d2e5fc"), na.translate = FALSE) +
  scale_x_continuous(labels = function(x) percent(round(x, 1))) +
  labs(x = "P(Correct)", y = "Posterior probability density", fill = "CrI") +
  theme(
    legend.position = c(1, 0.25),
    legend.direction = "vertical",
    legend.background = element_rect(fill = "grey95"),
    legend.key = element_rect(fill = "grey95", colour = "grey95"), 
    legend.key.height = unit(0.1, "cm"),
    axis.title.y = element_blank(),
    legend.text = element_text(size = 7),
    axis.text.x = element_text(colour = "black"),
    axis.text.y = element_text(colour = "black", hjust = 1),
    axis.ticks.y = element_blank(),
    panel.grid.major.y = element_line(colour = "grey", size = 0.5)
  )

# SD of random effects
post_sd_data <- posterior_draws_fixed %>% 
  filter(str_detect(.variable, "sd_")) %>% 
  mutate(
    .variable_name = str_remove(.variable, "sd_participant__|sd_word__") %>% 
      str_replace_all(str_repl) %>% 
      factor(
        levels = c(
          "Intercept", "Frequency\n[+1 SD]", "PTHN\n[+1 SD]", 
          "Levenshtein\n[+1 SD]", "PTHN \u00d7 Levenshtein",
          "Group 1\n[ENG-* vs. SPA-CAT]",
          "Group 2\n[ENG-CAT vs. ENG-SPA]",
          "Levenshtein \u00d7 Group 1", "Levenshtein \u00d7 Group 2"
        )
      ),
    group = case_when(
      str_detect(.variable, "participant") ~ "Participants",
      str_detect(.variable, "word") ~ "Words"
    ),
    .value = ifelse(str_detect(.variable, "Intercept"), inv_logit_scaled(.value), .value/4)
  )

@@

```{r post_re_participant, echo=FALSE, fig.height=6, fig.width=9, message=FALSE, warning=FALSE, paged.print=FALSE}
post_re <- posterior_draws_random$participants %>% 
  mean_qi() %>% 
  ungroup() %>% 
  left_join(select(participants, participant, group)) %>% 
  arrange(group, participant, .param) %>% 
  mutate(.param_name = str_replace_all(.param, str_repl) %>%  
           factor(
             levels = c(
               "Intercept", "Frequency\n[+1 SD]", "PTHN\n[+1 SD]", 
               "Levenshtein\n[+1 SD]", "PTHN \u00d7 Levenshtein",
               "Group 1\n[ENG-* vs. SPA-CAT]",
               "Group 2\n[ENG-CAT vs. ENG-SPA]",
               "Levenshtein \u00d7 Group 1", "Levenshtein \u00d7 Group 2"
             )
           ))

@@

post_re <- posterior_draws_random$words   %>% 
  ungroup() %>% 
  arrange(word, .param) %>% 
  mutate(
    .param_name = str_replace_all(.param, str_repl) %>%  
      factor(
        levels = c(
          "Intercept", "Frequency\n[+1 SD]", "PTHN\n[+1 SD]", 
          "Levenshtein\n[+1 SD]", "PTHN \u00d7 Levenshtein",
          "Group 1\n[ENG-* vs. SPA-CAT]",
          "Group 2\n[ENG-CAT vs. ENG-SPA]",
          "Levenshtein \u00d7 Group 1", "Levenshtein \u00d7 Group 2"
        )
      ),
    .value = inv_logit_scaled(.value)
  )

>>>>

str_repl <- c(
  "Intercept" = "Intercept",
  "frequency_zipf_std" = "Frequency\n[+1 SD]",
  "pthn_std:lv_std" = "PTHN \u00d7 Levenshtein", 
  "lv_std:group1" = "Levenshtein \u00d7 Group 1",
  "lv_std:group2" = "Levenshtein \u00d7 Group 2",
  "lv_std" = "Levenshtein\n[+1 SD]",
  "pthn_std" = "PTHN\n[+1 SD]",
  "group1" =  "Group 1\n[*-ENG vs. cat-SPA]",
  "group2" = "Group 2\n[cat-ENG vs. spa-ENG]"
)

coefs %>% 
  mutate(
    variable = str_remove(variable, "b_") %>% 
      str_replace_all(str_repl) %>%  
      factor(
        levels = c(
          "Intercept", 
          "Frequency\n[+1 SD]",
          "PTHN\n[+1 SD]", 
          "Levenshtein\n[+1 SD]", 
          "PTHN \u00d7 Levenshtein",
          "Group 1\n[cat/spa-ENG vs. cat-SPA]",
          "Group 2\n[cat-ENG vs. spa-ENG]",
          "Levenshtein \u00d7 Group 1",
          "Levenshtein \u00d7 Group 2"
        )
      )
  ) %>% 
  select(-est_error) %>% 
  gt() %>% 
  fmt_percent(2:4) %>% 
  cols_merge(c("q2_5", "q97_5"), pattern = "[{1}, {2}]") %>% 
  cols_label(
    variable = md("**Predictor**"),
    estimate = md("**Mean**"),
    q2_5 = md("**95\\% CrI**"),
  ) %>% 
  tab_source_note("Estimated posterior distributions of coefficients in Model 6. A\\) Population-level effects. Distributions indicate the estimated posterior likelihood density of regression coefficients of fixed effects. Credible intervals (*CrI*), represented with increasingly lighter segmentents in the distribution indicate the range of values that contain the true value with 95\\%, 80\\%, and 50\\% probability. Black dots represent the mean of each distribution.") %>% 
  cols_align(align = "left") %>% 
  as_raw_html()
```

@@

str_repl <- c(
  "Intercept" = "Intercept",
  "frequency_zipf_std" = "Frequency\n[+1 SD]",
  "pthn_std:lv_std" = "PTHN \u00d7 Levenshtein", 
  "lv_std:group1" = "Levenshtein \u00d7 Group 1",
  "lv_std:group2" = "Levenshtein \u00d7 Group 2",
  "lv_std" = "Levenshtein\n[+1 SD]",
  "pthn_std" = "PTHN\n[+1 SD]",
  "group1" =  "Group 1\n[*-ENG vs. cat-SPA]",
  "group2" = "Group 2\n[cat-ENG vs. spa-ENG]"
)

# fixed effects
post_fix <- posterior_draws_fixed %>% 
  filter(str_detect(.variable, "b_")) %>% 
  mutate(
    .variable_name = str_remove(.variable, "b_") %>% 
      str_replace_all(str_repl) %>%  
      factor(
        levels =c(
          "Intercept", 
          "Frequency\n[+1 SD]",
          "PTHN\n[+1 SD]", 
          "Levenshtein\n[+1 SD]", 
          "PTHN \u00d7 Levenshtein",
          "Group 1\n[cat/spa-ENG vs. cat-SPA]",
          "Group 2\n[cat-ENG vs. spa-ENG]",
          "Levenshtein \u00d7 Group 1",
          "Levenshtein \u00d7 Group 2"
        )
      ),
    .value = ifelse(str_detect(.variable, "Intercept"), inv_logit_scaled(.value), .value/4)
  ) %>% 
  arrange(.variable) %>% 
  ggplot(aes(.value, fct_rev(.variable_name))) +
  geom_vline(xintercept = 0) +
  stat_slab(aes(fill = stat(cut_cdf_qi(cdf, .width = c(.5, .8, .95), labels = percent_format())))) +
  stat_pointinterval(.width = 0, point_size = 1) +
  scale_fill_manual(values = c("#1A85FF", "#9ccaff", "#d2e5fc"), na.translate = FALSE) +
  scale_x_continuous(labels = function(x) percent(round(x, 1))) +
  labs(x = "P(Correct)", y = "Posterior probability density", fill = "CrI") +
  theme(
    legend.position = c(1, 0.25),
    legend.direction = "vertical",
    legend.background = element_rect(fill = "grey95"),
    legend.key = element_rect(fill = "grey95", colour = "grey95"), 
    legend.key.height = unit(0.1, "cm"),
    axis.title.y = element_blank(),
    legend.text = element_text(size = 7),
    axis.text.x = element_text(colour = "black"),
    axis.text.y = element_text(colour = "black", hjust = 1),
    axis.ticks.y = element_blank(),
    panel.grid.major.y = element_line(colour = "grey", size = 0.5)
  )

# SD of random effects
post_sd_data <- posterior_draws_fixed %>% 
  filter(str_detect(.variable, "sd_")) %>% 
  mutate(
    .variable_name = str_remove(.variable, "sd_participant__|sd_word__") %>% 
      str_replace_all(str_repl) %>% 
      factor(
        levels = c(
          "Intercept", 
          "Frequency\n[+1 SD]",
          "PTHN\n[+1 SD]", 
          "Levenshtein\n[+1 SD]", 
          "PTHN \u00d7 Levenshtein",
          "Group 1\n[cat/spa-ENG vs. cat-SPA]",
          "Group 2\n[cat-ENG vs. spa-ENG]",
          "Levenshtein \u00d7 Group 1",
          "Levenshtein \u00d7 Group 2"
        )
      ),
    group = case_when(
      str_detect(.variable, "participant") ~ "Participants",
      str_detect(.variable, "word") ~ "Words"
    ),
    .value = ifelse(str_detect(.variable, "Intercept"), inv_logit_scaled(.value), .value/4)
  )

@@

```{r post_re_participant, echo=FALSE, fig.height=6, fig.width=9, message=FALSE, warning=FALSE, paged.print=FALSE}
post_re <- posterior_draws_random$participants %>% 
  mean_qi() %>% 
  ungroup() %>% 
  left_join(select(participants, participant, group)) %>% 
  arrange(group, participant, .param) %>% 
  mutate(.param_name = str_replace_all(.param, str_repl) %>%  
           factor(
             levels = c(
          "Intercept", 
          "Frequency\n[+1 SD]",
          "PTHN\n[+1 SD]", 
          "Levenshtein\n[+1 SD]", 
          "PTHN \u00d7 Levenshtein",
          "Group 1\n[cat/spa-ENG vs. cat-SPA]",
          "Group 2\n[cat-ENG vs. spa-ENG]",
          "Levenshtein \u00d7 Group 1",
          "Levenshtein \u00d7 Group 2"
        )
           )
        )

@@

post_re <- posterior_draws_random$words   %>% 
  ungroup() %>% 
  arrange(word, .param) %>% 
  mutate(
    .param_name = str_replace_all(.param, str_repl) %>%  
      factor(
        levels = c(
          "Intercept", 
          "Frequency\n[+1 SD]",
          "PTHN\n[+1 SD]", 
          "Levenshtein\n[+1 SD]", 
          "PTHN \u00d7 Levenshtein",
          "Group 1\n[cat/spa-ENG vs. cat-SPA]",
          "Group 2\n[cat-ENG vs. spa-ENG]",
          "Levenshtein \u00d7 Group 1",
          "Levenshtein \u00d7 Group 2"
        )
      ),
    .value = inv_logit_scaled(.value)
  )
